Mapping Microblog Posts to Encyclopedia Articles

### 2011-03-03 lids/twittersearchwrap/paper/paper.tex

@@

Wagner \cite{key:clauwa} proposes to use aggregations of social awareness streams for knowledge extraction.
As such, our approach is closely related.
Stankovic et al. \cite{key:stanko} propose to use the Zemanta\footnote{\url{http://developer.zemanta.com/}} keyword extraction API to detect topics of single Twitter messages.
% from stakovic et al.
%In order to make tweets more searchable and make them useful for the described
%scenario one would need to have represent them in a structured format and associate
%those tweets with the topics that refer to. As a basic approach we process the text of
%the tweets using Zemanta16 keyword extraction API. This approach gives DBPedia
%concepts related to a tweet, but is useful only on a limited number of tweets directly
%mentioning a particular topic. In the example data set we produced from ESWC2010,
%tweet topics are represented using dc:subject property.

@@

Trending topics are listed in Table \ref{tbl:terms}.

\begin{table}[ht*]
\centering
\begin{tabular}{ c }
Search term                    \\
\hline
\#s21 \\
Karlsruhe\\
\end{tabular}
\caption{Search terms}\label{tbl:terms}
\end{table}

@@

The goal of our evaluation was to examine the stability of the entity annotations over time. To achieve this, we have repeatedly executed the same set of queries. \myremark{TODO}{How frequently? How long? Which queries?}
In a first step we have filtered the result sets such that each set is disjoint to all the other sets for the same query with respect to the messages it contains. We have then evaluated the results with respect to several measures:

>>>>

\setlength{\tabcolsep}{2pt}

@@

Softic et al \cite{key:softic} have developed a framework and system for mining
data from social networks. They have instantiated their system to analyze data from Twitter. In their system, they collect data from one or several users. The system by Passant et al. \cite{key:smob} is used for transforming twitter data to semantic data. The triplified data can then be analysed using SPARQL. They propose that the result data could be enriched using entities from other Linked Open data vocabularies like dbpedia\footnote{\url{http://dbpedia.org}} or GeoNames\footnote{\url{http://www.geonames.org}}, but they do not provide a method for achieving this.
Wagner \cite{key:clauwa} proposes to use aggregations of social awareness streams for knowledge extraction.
As such, our approach is closely related.
Stankovic et al. \cite{key:stanko} propose to use the Zemanta\footnote{\url{http://developer.zemanta.com/}} keyword extraction API to detect topics of single Twitter messages.
% from stakovic et al.
%In order to make tweets more searchable and make them useful for the described
%scenario one would need to have represent them in a structured format and associate
%those tweets with the topics that refer to. As a basic approach we process the text of
%the tweets using Zemanta16 keyword extraction API. This approach gives DBPedia
%concepts related to a tweet, but is useful only on a limited number of tweets directly
%mentioning a particular topic. In the example data set we produced from ESWC2010,
%tweet topics are represented using dc:subject property.

@@

Topics trending worldwide and in Germany at Twitter retrieved at February 24th
17:20h (GMT) are listed in Table \ref{tbl:terms}. These trending topics will
constitute a basis of input search terms for our evaluation of the Twitter
Search Wrapper.

\begin{table}[ht*]
\centering
\begin{tabular}{ |l|l| }
\hline
\textsc{Trending Topic} & \textsc{Location}  \\
\hline
\#goodlucknickj & Worldwide \\
\#smalljoys & Worldwide \\
\#thingsthedevilinvented & Worldwide \\
Adam Wainwright & Worldwide \\
CatchPetrovaFire & Worldwide \\
Gadafi & Worldwide \\
Libia & Worldwide \\
Precious Minaj & Worldwide \\
Tommy John & Worldwide \\
\hline
\#gaddafi & Germany \\
\#guttenberg & Germany \\
\#libya & Germany \\
Doktorarbeit & Germany \\
Gef\"{u}hl & Germany \\
Lion & Germany \\
MBP & Germany \\
Thunderbolt & Germany \\
Vorratsdatenspeicherung & Germany \\
\hline
\end{tabular}
\caption{Search terms}\label{tbl:terms}
\end{table}

@@

The goal of our evaluation was to examine the stability of the entity
annotations over time. To achieve this, we have repeatedly executed the same set
of queries using the retrieved trending topics given in Table \ref{tbl:terms}
as input queries for the evaluation. The set of queries was executed twice per
hour in a 24 hour time frame starting from the moment the topics were identified
and retrieved as trending topics. In a first step we have filtered the result
sets such that each set is disjoint to all the other sets for the same query with respect to the messages it contains. We have then evaluated the results with respect to several measures:
